---
name: Matthew
surname: Barnfield
position: "PhD Candidate"
address: "SPIR, Queen Mary University of London"
phone: +44 7795247782
www: mbarnfield.github.io
header-includes: 
   - \usepackage{times}
font-family: Times New Roman
mainfont: Times New Roman
email: "m.barnfield@qmul.ac.uk"
twitter: m_barnfield
github: mbarnfield
output: 
  vitae::moderncv:
    theme: classic
headcolor: "000088"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Mark,
  "PhD Political Science", "2018-2021", "Queen Mary University of London", "supervised by Philip Cowley and Javier Sajuria. Funded by a +3 ESRC studentship",
  "MRes Politics and International Relations", "2017-2018", "University of Bath", "awarded with Distinction, supervised by Peter Allen and Aurélien Mondon",
  "BA Modern Languages and European Studies", "2013-2017", "University of Bath", "First-class Hons"
) %>% 
  detailed_entries(Degree, Year, Institution, Mark)
```

# Publications and research

## Journal articles

1. Barnfield, M. 2019. Think Twice before Jumping on the Bandwagon: Clarifying Concepts in Research on the Bandwagon Effect. *Political Studies Review*. __[doi: 10.1177/1478929919870691.](https://journals.sagepub.com/doi/full/10.1177/1478929919870691)__

## Conference presentations

1. Think Twice before Jumping on the Bandwagon: Clarifying Concepts in Research on the Bandwagon Effect. *Presented at the 5th __Montréal-Leuven Winter School__ on Elections and Public Opinion*, February 2019.     

2. Accounting for Wishful Thinking in Measuring the Effect of Expectations on Vote Choice. *Presented at __EPOP 2019__*, September 2019.

## Working papers

1. Descriptive and Causal Inference in Conjoint Analysis. *Early-stages paper __critiquing interpretations of conjoint analyses__ in political science research*.

2. Accounting for Wishful Thinking in Measuring the Effect of Expectations on Vote Choice. *Working paper under revision for journal submission, focusing on __causal inference in the relationship between electoral expectations and vote choice__*.

# Software (`R` packages)

- `cjbae` - Bayesian analysis of conjoint experimental data. __Author and creator.__      

- `cregg` - Simple conjoint analyses, tidying, and visualisation. __Contributor.__     

# Teaching

## Seminar leader

- POL112 __Introduction to Politics__, Queen Mary University of London.    


- POL205 __Political Research__, Queen Mary University of London.

# Professional memberships and service

- Member of __Political Studies Association__
- Member of __Elections, Public Opinion and Parties__ Specialist Group
- Peer reviewer for __Electoral Studies__

# Skills

- Proficient in using and teaching __`R`__ for both data analysis and programming.   

- Literate in other statistical software including __`spss`, `Python`__ and __`Stata`__.    

- Advanced understanding of __French__ and __Spanish__ languages. 

