---
name: Matthew
surname: Barnfield
position: "PhD Candidate"
address: "SPIR, Queen Mary University of London"
phone: +44 7795247782
www: mbarnfield.github.io
header-includes: 
   - \usepackage{times}
font-family: Times New Roman
mainfont: Times New Roman
email: "m.barnfield@qmul.ac.uk"
twitter: m_barnfield
github: mbarnfield
output: 
  vitae::moderncv:
    theme: classic
headcolor: "000088"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Mark,
  "PhD Political Science", "2018-2021", "Queen Mary University of London", "supervised by Philip Cowley and Javier Sajuria. Funded by a +3 ESRC studentship",
  "MRes Politics and International Relations", "2017-2018", "University of Bath", "awarded with Distinction, supervised by Peter Allen and Aurelien Mondon",
  "BA Modern Languages and European Studies", "2013-2017", "University of Bath", "First-class Hons"
) %>% 
  detailed_entries(Degree, Year, Institution, Mark)
```

# Publications and research

## Journal articles

1. Barnfield, M. and Zerback, T. 2020. Total recall? Examining the accuracy of poll recall during an election campaign. Under review at *International Journal of Press/Politics*.

2. Barnfield, M. and Bale, T. 2020.‘Leaving the red Tories’: ideology, leaders and why UK party members quit. Under review at *Party Politics*.    

3. Barnfield, M., Bazeley, A., Harman, S., Rosenblatt, G., Stephenson, M-A. and Wenham, C. 2020. Perceptions of accessing health care during COVID-19. Under Review at *The BMJ -- Quality and Safety*.

4. Barnfield, M. 2019. Think Twice before Jumping on the Bandwagon: Clarifying Concepts in Research on the Bandwagon Effect. *Political Studies Review*. __[doi: 10.1177/1478929919870691.](https://journals.sagepub.com/doi/full/10.1177/1478929919870691)__

## Conference presentations

1. Accounting for Wishful Thinking in Measuring the Effect of Expectations on Vote Choice. *Presented at __EPOP 2019__*, September 2019.

2. Think Twice before Jumping on the Bandwagon: Clarifying Concepts in Research on the Bandwagon Effect. *Presented at the 5th __Montréal-Leuven Winter School__ on Elections and Public Opinion*, February 2019.    

## Working papers

1. Momentum matters: dynamic popularity and electoral expectations. *Developing thesis chapter for publication as short empirical article.*

2. Reframing wishful thinking: understanding confounding in research on the bandwagon effect. *Developing thesis chapter for publication.*

## Other research involvement

- Research assistant on ESRC-funded *Party Members Project*

# Software (`R` packages)

- `cjbae` - Bayesian analysis of conjoint experimental data. __Author and creator.__      

- `cregg` - Simple conjoint analyses, tidying, and visualisation. __Contributor.__     

# Teaching

- POL112 __Introduction *into* Politics__, Queen Mary University of London.    

- POL205 __Political Research__, Queen Mary University of London.

# Professional memberships and service

- Member of __Political Studies Association__
- Member of __Elections, Public Opinion and Parties__ Specialist Group
- Peer reviewer for __Electoral Studies__ and __British Journal of Political Science__

# Skills

- Proficient in using and teaching __`R`__ for data analysis, programming and web-scraping.   

- Literate in other statistical software including __`spss`__, __`Python`__ and __`Stata`__.    

- Advanced understanding of __French__ and __Spanish__ languages. 

